Final Project

### 2025-04-24 MSSC5750_Project.qmd
Update MSSC5750_Project.qmd

```{r echo = FALSE, message=FALSE}
library(MASS)
library(ggplot2)
library(dplyr)
library(scales)
library(glmnet)
library(fastDummies)
library(caret)

@@

# One-hot-encoding our categorical variables. Should happen automatically for factors
data$person_gender <- as.factor(data$person_gender)
data$person_home_ownership<-as.factor(data$person_home_ownership)
data$loan_intent<-as.factor(data$loan_intent)
data$previous_loan_defaults_on_file<-as.factor(data$previous_loan_defaults_on_file)

>>>>

```{r echo = FALSE, message=FALSE}
library(MASS)
library(ggplot2)
library(dplyr)
library(scales)
library(glmnet)
library(fastDummies)
library(caret)
#

@@

# Preparing categorical variables. Should happen automatically for factors
data$person_gender <- as.factor(data$person_gender)
data$person_home_ownership<-as.factor(data$person_home_ownership)
data$loan_intent<-as.factor(data$loan_intent)
data$previous_loan_defaults_on_file<-as.factor(data$previous_loan_defaults_on_file)
